

###### OUTTAKES ########

### RESULTS

## To prepare in advance:

- add columns to the dataset: would have testing of assumptions been necessary?


## Aim 1: Analysis

Calculate reporting frequencies of
- precise statement if it was applied on a trial-level, averaged first asf.
- a rationale behind the data transformation
- assumption testing
- outlier and criterion
- open science practices?
- specific statistical models?

Maybe identify patterns across studies
- Do studies that report one data transformation aspect also report the others? -> e.g., if trial-level, then also rationale
-> possible plot: spider

## Möglicher Aufbau
### a. Descriptives (Replication? in Supplementary)
n_with_exclusions, n_female_total, age_mean_total, age_sd_total, mental health disorder exclusion, Was an individual level analysis conducted

### b. Assumption Checking (am Beispiel hier mit Normality)
- Welches Statistische Verfahren vorgeschaltet? 
- Mario konsultieren
eine Frage -> dann Sanky mit Antwort und Anzahl, Tina/Mana bars, doughnuts, lolli, waffle/heatmap e.g., Was the normal distribution checked?, If yes, how?, before/after, etc.
FRAGEN
- Was the normal distribution checked?
- Was the homoscedasticity checked?
- Was the sphericity checked?
- Was the independence of residuals checked?
- Was the linearity checked?
- Was the multicollinearity checked?

```{r results-assumptions}
### Assumption: Normal distribution
# Extract an rename the data
normal_distr_data <- data_extract[ ,c(20:22)]
names(normal_distr_data) <- c("normal_if","normal_how","normal_when")

# Convert to long format
normal_distr_data <- normal_distr_data %>%
  make_long(normal_if,normal_how,normal_when)

# Plot the Sankey diagram
ggplot(normal_distr_data, aes(x = x, 
                    next_x = next_x, 
                    node = node, 
                    next_node = next_node, 
                    fill = factor(node))) +
  geom_sankey(flow.alpha = 0.7, node.color = 1) +
  scale_fill_viridis_d(option = "A", alpha = 0.95) +
  theme_sankey(base_size = 16)

```


```{r re-transf}
# reference for transformation type?
# Load required libraries
library(tidyverse)
library(scico)
library(forcats)
library(scales)
library(patchwork)

# Load the relevant data
#data.frame(colname = data_extract %>% colnames()) %>% mutate(colnum = 1:n()) %>% relocate(colnum)
df_ref <- data_extract %>% select(rationale_given = dt_rationale, rationale_type = dt_rationale_details)

# -------------------------
# PIE 1: Was a rationale reported?
# -------------------------
df_pie1 <- df_ref %>%
  count(response = rationale_given) %>%
  filter(!is.na(response) & response != "") %>%
  mutate(
    percent = n / sum(n),
    label = paste0(response, "\n", n, " (", percent(percent, accuracy = 1), ")"),
    ymax = cumsum(percent),
    ymin = lag(ymax, default = 0),
    label_pos = (ymin + ymax) / 2
  )

plot1 <- ggplot(df_pie1, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = response)) +
  geom_rect(color = "white") +
  geom_text(aes(x = 1.2, y = label_pos, label = label), size = 4.5, color = "black", fontface = "bold") +
  coord_polar(theta = "y") +
  xlim(c(-0.5, 1.5)) +
  scale_fill_scico_d(palette = "roma", direction = -1) +
  theme_void(base_family = "Helvetica") +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold", hjust = 0)
  ) +
  labs(title = "Was a Rationale for Transformation Reported?")

# -------------------------
# PIE 2: What kind of rationale (only for 'yes')
# -------------------------
df_pie2 <- df_ref %>%
  filter(tolower(rationale_given) == "yes", !is.na(rationale_type), rationale_type != "") %>%
  count(response = rationale_type) %>%
  mutate(
    percent = n / sum(n),
    label = paste0(response, "\n", n, " (", percent(percent, accuracy = 1), ")"),
    ymax = cumsum(percent),
    ymin = lag(ymax, default = 0),
    label_pos = (ymin + ymax) / 2
  )

plot2 <- ggplot(df_pie2, aes(ymax = ymax, ymin = ymin, xmax = 1, xmin = 0, fill = response)) +
  geom_rect(color = "white") +
  geom_text(aes(x = 1.2, y = label_pos, label = label), size = 4.5, color = "black", fontface = "bold") +
  coord_polar(theta = "y") +
  xlim(c(-0.5, 1.5)) +
  scale_fill_scico_d(palette = "roma", direction = -1) +
  theme_void(base_family = "Helvetica") +
  theme(
    legend.position = "none",
    plot.title = element_text(size = 16, face = "bold", hjust = 0)
  ) +
  labs(title = "What Kind of Rationale Was Given?")

# -------------------------
# Combine both plots
# -------------------------
plot1 / plot2 + plot_layout(heights = c(1, 1.2))


# Prepare data
df_bar1 <- df_ref %>%
  count(response = rationale_given) %>%
  filter(!is.na(response) & response != "") %>%
  mutate(
    percent = n / sum(n),
    label = paste0(" (", percent(round(percent, digits = 3)), ")"),
    response = fct_reorder(response, n)
  )

# Create modern bar plot
ggplot(df_bar1, aes(x = fct_rev(response), y = percent, fill = response)) +
  geom_col(width = 0.6, alpha = 0.9) +
  geom_text(aes(label = label), hjust = -0.1, size = 4.5, color = "gray20", fontface = "bold") +
  coord_flip() +
  scale_y_continuous(labels = percent_format(accuracy = 1), expand = expansion(mult = c(0, 0.2))) +
  scale_fill_scico_d(palette = "roma", direction = -1, guide = "none") +
  theme_classic(base_size = 15) +
  theme(
    axis.title = element_blank(),
    axis.text = element_text(color = "gray10"),
    plot.title = element_text(size = 16, face = "bold", hjust = 0)
  ) +
  labs(title = "Was a Rationale for Transformation Reported?")


```


```{r results-individual-level-analysis}

## Table the column with individual level analysis info
table_ind_analysis <- data_extract[grep("individual.level.analysis", names(data_extract))]
table_ind_analysis <- table_ind_analysis[ ,1]
table_ind_analysis <- as.data.frame(table(table_ind_analysis))
colnames(table_ind_analysis) <- c("category", "count")


# Compute percentages
table_ind_analysis$fraction <- table_ind_analysis$count / sum(table_ind_analysis$count)

# Compute the cumulative percentages (top of each rectangle)
table_ind_analysis$ymax <- cumsum(table_ind_analysis$fraction)

# Compute the bottom of each rectangle
table_ind_analysis$ymin <- c(0, head(table_ind_analysis$ymax, n=-1))

# Compute label position
table_ind_analysis$labelPosition <- (table_ind_analysis$ymax + table_ind_analysis$ymin) / 2

# Compute a good label
table_ind_analysis$label <- paste0(table_ind_analysis$category, ": ", table_ind_analysis$count)

# Create the plot
ggplot(table_ind_analysis, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category)) +
  geom_rect() +
  geom_label(x = 3.5, aes(y = labelPosition, label = label), size = 6) +
  scale_fill_brewer(palette = "Set3") +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  ggtitle("Individual analysis included?") +
  theme_void() +
  theme(legend.position = "none")

```


### e. Outcome Measures
Binary presence/absence analysis
pattern identifizieren
the use of different psychophysioligical outcomes?scr, emg 
dot-plot-simulation

```{r results-outcome-measures}
#data.frame(colname = data_extract %>% colnames()) %>% mutate(colnum = 1:n()) %>% relocate(colnum)
data_outcome_measure <- data_extract %>%
  select(`HR`:PUPIL_SIZE) %>%
  rename(
   #"HR" = HR (BPM)
   #"EMG orbicularis oculi" = EMG.orbicularis.oculi,
   #"EMG startle" = EMG.startle,
  ## "EYE tracking" = EYE.tracking,
   #"pupil size" = PUPIL.SIZE
  ) %>%
  filter(!if_all(everything(), ~ is.na(.) | . == "")) %>%
  mutate(id = row_number()) %>%  # Add ID if no group exists
  pivot_longer(
    cols = -id,
    names_to = "Measure",
    values_to = "Transformation"
  ) %>%
  drop_na(Transformation) %>%
  count(Measure, Transformation) %>%
  group_by(Measure) %>%
  mutate(
    percent = n / sum(n),
    label = scales::percent(percent)
  )

ggplot(data_outcome_measure, aes(x = factor(Measure), y = n, fill = Transformation)) +
  geom_bar(stat = "identity") +
  scale_fill_viridis_d(option = "A", alpha = 0.95) +
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.5), 
            color = "white", size = 4, fontface = "bold") +
  lit_theme +
  theme(#axis.text.y = element_blank(),
        #axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        #axis.title.y = element_blank(),
        legend.position = "top")+
  coord_flip()+
  labs(y = "n studies")

### add combinations of data transformations

```


### f. Statistical Models
Statistical model, Main statistical test, further specification
- Count and visualize test types (t-test, ANOVA, mixed models)
- Compare test choice across study types or transformation practices
- Association with whether assumptions were tested

```{r results-statistical-models}
#data.frame(colname = data_extract %>% colnames()) %>% mutate(colnum = 1:n()) %>% relocate(colnum)
data_stat_models <- data_extract %>%
  select(design:statistical_test_details) %>%
  filter(!if_all(everything(), ~ is.na(.) | . == ""))%>%
  make_long(design, `levels of largest within factor`, `statistical test`, `statistical test details`)%>%
  filter(!if_all(c(node), is.na))

ggplot(data_stat_models, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey(flow.alpha = 0.5, node.color = 1) +
  geom_sankey_label(size = 4, color = 1, fill = "white") +
  scale_fill_viridis_d(option = "A", alpha = 0.95) +
  lit_theme + 
  theme(axis.text.y = element_blank(),
                    axis.ticks.y = element_blank(),
                    axis.title.x = element_blank())
```



```{r results-mental-health}

## Table the column with mental health info
table_health_info <- as.data.frame(table(data_extract[grep("mental.health.disorder", names(data_extract))]))
colnames(table_health_info) <- c("category", "count")


# Compute percentages
table_health_info$fraction <- table_health_info$count / sum(table_health_info$count)

# Compute the cumulative percentages (top of each rectangle)
table_health_info$ymax <- cumsum(table_health_info$fraction)

# Compute the bottom of each rectangle
table_health_info$ymin <- c(0, head(table_health_info$ymax, n=-1))

# Compute label position
table_health_info$labelPosition <- (table_health_info$ymax + table_health_info$ymin) / 2

# Compute a good label
table_health_info$label <- paste0(table_health_info$category, ": ", table_health_info$count)

# Create the plot
ggplot(table_health_info, aes(ymax = ymax, ymin = ymin, xmax = 4, xmin = 3, fill=category)) +
  geom_rect() +
  geom_label(x = 3.5, aes(y = labelPosition, label = label), size = 6) +
  scale_fill_brewer(palette = "Set2") +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  ggtitle("Mental health disorder exclusion?") +
  theme_void() +
  theme(legend.position = "none")


```


